A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-10 main.tex
Wrote the first paragraph of Conclusions.

>>>>

We proposed new multi-stage calculus \LMD, which can use dependent types.
\LMD enable finer-grained typing of multi-stage programming comparing to existing type systems.
This extention prevent some bugs relating to generated functions with multi-stage programming,
such as \verb|vadd| function for vectors of a fixed length.
We proved properties of \LMD including preservation, confluence, 
strong normalization for full reduction, and progress for staged reduction.
The technical difficulty of extention is how to deal with the symbol of CSP $\%$ in the equation rules.
We resolve this problem by ignoring $\%$ under some condition.
